Initial Guess

### 2020-04-24 LaTeX_Code/Paper/paper_1line.tex
Added tables with results in Chapters 5 and 6. The corresponding MATLAB files have also commented this results. Next time, I will add all the plots.

\begin{table}[H]
\centering
\begin{tabular}{cccc}
\toprule
Model   &  parameters $(\theta_0, \alpha,\delta)$   & AIC & BIC \\ \midrule
Model 1 &  $(\add,\add) $    &  \add   &  \add   \\
Model 2 &   $(1.2,0.1,0.6)$   &  \add   &   \add    \\ 
\bottomrule
\end{tabular}
\caption{We compare the different models based on information criterion. \add }
\label{tab:model_comparison}
\end{table}
%---END SECTION 5---

%---BEGIN SECTION 6---
\section{Forecast Provider Comparison} \label{Section_6}
We compare forecasts from two different companies for the same period.
\begin{table}[H]
\centering
\begin{tabular}{ccc}
\toprule
Forecast Provider & Parameters $(\theta_0, \alpha)$ & Product $\theta_0\alpha$ \\ \midrule
Provider A  &  $(1.180,0.070)$      &  0.083    \\
Provider B  & $(0.766,0.117) $  &  0.090 \\ 
Provider C  & $(1.347,0.073) $  &  0.099 \\ 
\bottomrule
\end{tabular}
\caption{\add}
\label{tab:forcast_comparison}
\end{table}

>>>>

\begin{table}[H]
\centering
\begin{tabular}{cccccc}
\toprule
Model & Forecast Provider & Method & Product $\theta_0\alpha$   & AIC & BIC \\ \midrule
Model 1 & Provider A & Gaussian Proxy & 0.105 & -58226 & -58211 \\
 &  & Shoji-Ozaki & 0.104 & -58226 & -58211 \\
 &  & Beta Proxy & 0.104 & -58286 & -58271 \\
 & Provider B & Gaussian Proxy & 0.105 & -58226   & -58211 \\
 &  & Shoji-Ozaki & 0.104 & -58226 & -58211 \\
 &  & Beta Proxy & 0.104 & -58288 & -58273 \\
 & Provider C & Gaussian Proxy & 0.105 & -58226 & -58211 \\
 &  & Shoji-Ozaki & 0.104 & -58226 & -58211 \\
 &  & Beta Proxy & 0.104 & -58286 & -58271 \\
Model 2 & Provider A & Beta Proxy & 0.097 & -73700   & -73685 \\ 
 & Provider B & Beta Proxy & 0.098 &  -73502 & -73487 \\ 
 & Provider C & Beta Proxy & 0.108 & -72518 & -72503 \\ 
\bottomrule
\end{tabular}
\caption{We compare the different models based on information criterion. \add }
\label{tab:model_comparison}
\end{table}
%---END SECTION 5---

%---BEGIN SECTION 6---
\section{Forecast Provider Comparison} \label{Section_6}
We compare forecasts from two different companies for the same period.
\begin{table}[H]
\centering
\begin{tabular}{ccc}
\toprule
Forecast Provider & Parameters $(\theta_0, \alpha)$ & Product $\theta_0\alpha$ \\ \midrule
Provider A  & $(1.930,0.050)$  &  0.097 \\
Provider B  & $(1.420,0.069) $  &  0.098 \\ 
Provider C  & $(1.380,0.078) $  &  0.108 \\ 
\bottomrule
\end{tabular}
\caption{Optimal parameters for different providers using Model 2 with Beta proxies.}
\label{tab:forcast_comparison}
\end{table}

### 2020-04-24 MATLAB_Files/MATLAB_readMe/MATLAB_readMe.tex
Added tables with results in Chapters 5 and 6. The corresponding MATLAB files have also commented this results. Next time, I will add all the plots.

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Density next measurement (2/2):}

@@

@@

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Density next measurement:}

@@

>>>>

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Density next measurement (2/2):}\label{Tr2}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Density next measurement:}\label{lamp_LH}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\Huge Model 1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Model 1 SDE:}

Given the SDE
\begin{equation*}
\dif X_t=\underbrace{-\theta_0\left(X_t-p_t\right)}_{:=\mu_t}\dif t+\underbrace{\sqrt{2\theta_0\alpha X_t(1-X_t)}}_{:=\sigma_t}\dif W_t,
\end{equation*}
we want to approximate its moments. Trivially, we have an exact ODE for the first moment for $t\in[t_0,t_1]$:
\begin{equation*}
\begin{cases}
\dif \E\left[X_t\right]=-\theta_0\left(\E\left[X_t\right]-p_t\right)\dif t\\
\E\left[X_{t_0}\right]=x_{t_0}.
\end{cases}
\end{equation*}
Now, we can define the process $f_t=f(X_t,t)=X^2_t$ and apply It\^o's lemma. We reach that
\begin{equation*}
\dif f_t=\left(\frac{\partial f}{\partial t}+\mu_t\frac{\partial f}{\partial x}+\frac{\sigma^2_t}{2}\frac{\partial^2f}{\partial x^2}\right)\dif t+\sigma_t\frac{\partial f}{\partial x}\dif W_t,
\end{equation*}
where $\frac{\partial f}{\partial x}=2x$, $\frac{\partial^2 f}{\partial x^2}=2$, and $\frac{\partial f}{\partial t}=0$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Model 1 SDE:}

Doing SOME substitutions, we reach
\begin{equation*}
\dif f_t=2\theta_0\left(X_t(\alpha+p_t)-X^2_t(1+\alpha)\right)\dif t+\sigma_t\frac{\partial f}{\partial x}\dif W_t.
\end{equation*}
Now, if we apply the expected value operator $\E[\cdot]$, we get
\begin{equation*}
\dif\E\left[X^2_t\right]=2\theta_0\left(\E\left[X_t\right](\alpha+p_t)-\E\left[X^2_t\right](1+\alpha)\right)\dif t,
\end{equation*}
which is the second moment ODE with IV $\E\left[X^2_t\right]=x_{t_0}^2$ for $t\in[t_0,t_1]$. Recall that $\V\left[X_t\right]=\E\left[X_t^2\right]-\E\left[X_t\right]^2$. As we will assume Gaussian proxies, we will use the Likelihood described in Slide {\color{blue}\ref{lamp_LH}}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Model 1 SDE:}

The forward Euler schemes are:
\begin{enumerate}

\item $m_1(s_{n})=m_1(s_{n-1})-\theta_0(m_1(s_{n-1})-p_{s_{n-1}})\Delta s.$

\item $m_2(s_{n})=m_2(s_{n-1})+2\theta_0\left(m_1(s_{n-1})(\alpha+p_{s_{n-1}})-m_2(s_{n-1})(1+\alpha)\right)\Delta s.$
\end{enumerate}

\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../moment_1_M1.m}
}\\
\bottomrule
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{|c|}
\toprule
{\tiny
\lstinputlisting{../moment_2_M1.m}
}\\
\bottomrule
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Model 1 SDE: Shoji-Ozaki method}
{\footnotesize
An extension of the method to Ozaki the more general case where the drift is allowed to depend on the time variable t, and also the diffusion coefficient can be varied is the method Shoji and Ozaki. Consider the stochastic differential equation:
\begin{equation*}
\dif X_t=f(t,X_t,\bm{\theta})\dif t+q(X_t,\bm{\theta})\dif W_t,\quad t\geq0,X_0=x_0,
\end{equation*}
the transition density for the Shoji-Ozaki method is Gaussian, we have that: $X_{t+\Delta t}|X_t=x\sim\mathcal{N}\left(A_{(t,x)}x,B^2_{(t,x)}\right)$, where:
\begin{equation*}
A_{(t,x)}=1+\frac{f(t,x)}{xL_t}\left(e^{L_t\Delta t}-1\right)+\frac{M_t}{xL^2_t}\left(e^{L_t\Delta t}-1-L_t\Delta t\right),
\end{equation*}
\begin{equation*}
B_{(t,x)}=g(x)\sqrt{\frac{e^{2L_t\Delta t}-1}{2L_t}},
\end{equation*}
with:
\begin{equation*}
L_t=\partial_xf(t,x)\quad\text{and}\quad M_t=\frac{g^2(x)}{2}\partial_{xx}f(t,x)+\partial_tf(t,x).
\end{equation*}}
{\tiny
\url{https://cran.r-project.org/web/packages/Sim.DiffProc/vignettes/fitsde.html}}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!10}
\begin{frame}\frametitle{Model 1 SDE: Beta as proxy}

Following the same idea as in Slides (\ref{Tr}) and (\ref{Tr2}), but using $[a,b]=[0,1]$, we get the moments matching:
\begin{itemize}
\item $\xi_1=\frac{-\mu\sigma^2+\mu^2-\mu^3}{\sigma^2}$ all evaluated at time $t_n$ (verified in \textbf{Mathematica 11.0}\footnote{File: {\color{blue}Model1\_Beta.nb}.}).
\item $\xi_2=\frac{(\mu-1)(\sigma^2-\mu+\mu^2)}{\sigma^2}$ all evaluated at time $t_n$ (verified in \textbf{Mathematica 11.0}).
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-04-24 Reports/20200308 - Initial Guess/20200308 - Initial Guess.tex
Added tables with results in Chapters 5 and 6. The corresponding MATLAB files have also commented this results. Next time, I will add all the plots.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=green!20}
\begin{frame}

{\Huge Model 1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{Least square minimization (LSM)}

We consider the transition $\Delta X_i=X_{i+1}-X_i$ with $\Delta t=t_{i+1}-t_i$. $(X_{i+1}|X_i)$ is a random variable which conditional mean can be approximated by the solution of the system
\begin{equation*}
\begin{cases}
\dif \E\left[X\right]&=-\theta_0\left(\E\left[X\right]-p_t\right)\dif t\\
\E\left[X(t_i)\right]&=X_i,
\end{cases}
\end{equation*}
evaluated in $t_{i+1}$ (i.e., $\E\left[X(t_{i+1})\right]$). Then, the random variable $(X_{i+1}-\E\left[X(t_{i+1})\right])$ has approximately zero mean.\\
\quad\\
We consider the IVP $\dif x=-\theta_0(x-p_t)\dif t$ with initial conditions $x(t_i)=x_i$. Also, from now we will assume $t_i=0$.
\begin{theorem}
The ODE $\dot{y}=a(t)y+b(t)$ has solution $y(t)=ce^{A(t)}+e^{A(t)}\int e^{-A(t)}b(t)\dif t$ where $c\in\R$ and $A(t)=\int a(t)\dif t$.
\end{theorem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{Least square minimization (LSM) and Quadratic Variation}

$x(t)=ce^{-\theta_0 t}+e^{-\theta_0 t}\int e^{\theta_0 t}\theta_0p_t\dif t$ using the theorem. Now, recall that $p=p_i+\frac{(p_{i+1}-p_i)}{\Delta t}y=n+m\cdot y$ (we define $n$ and $m$ for simplicity).\\
\quad\\
Then: $x(t)=x_ie^{-\theta_0t}+\theta_0e^{-\theta_0t}\left[\frac{m+(e^{\theta_0t}-1)n\theta_0+e^{\theta_0t}m(\theta_0t-1)}{\theta_0^2}\right]$, where $x(t_{i+1})=\E\left[X(t_{i+1})\right]$.

\begin{equation*}
\theta_0^*\approx\arg\min_{\theta_0\geq0}\left[\sum_{i=1}^n\left(X_{i+1}-\E\left[X(t_{i+1})\right]\right)^2\right].
\end{equation*}\\
\quad\\
\quad\\
Quadratic Variation: To estimate $\theta_0\alpha$, we use equation (\ref{Eq-2}) but using $\Delta X$ instead of $\Delta V$, $X$ instead of $V$, and $0$ instead of $p$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setbeamercolor{background canvas}{bg=white!20}
\begin{frame}\frametitle{Why $\theta_0<0$?}

\includegraphics[width=0.7\columnwidth]{20200422_205641.jpg}
